### 2022-09-28 manuscript/manuscript.tex
few more minor changes

\subsection*{Effective Population Size for Pairwise Diversity}

@@

in the limit where $\mu \to 0$. This is equation 4 of
\textcite{Santiago2016-mu}; they define the sum the heterozygosity effective
population size.

Throughout, we assume that there is a constant \emph{drift-effective}
population size, $N_d$, which determines the rate of coalescence due only to
neutral demographic processes. We then consider the observed levels of neutral
pairwise diversity as a reduction factor down from the drift effective
population size, e.g. $\pi \approx 4 N_e \mu = 4 B N_d \mu$, where $B$ is a
reduction factor due to the background selection process.

>>>>

\subsection*{Pairwise Diversity under Background Selection}

@@

in the limit where $\mu \to 0$. This is equation 4 of
\textcite{Santiago2016-mu}; they define the sum as the heterozygosity effective
population size.

\subsection*{Forward in Time Models of Background Selection}

Next, show how quantitative genetic models of linked selection
\parencite{Robertson1961-ho,Santiago1995-hx,Santiago1998-bs,Santiago2016-mu}
model $b(t)$ forward in time.

\begin{align}
  b(t) = \frac{N_v}{N_d}
\end{align}

where

\begin{align}
  N_v = \lim_{t \to \infty} \frac{p_0 (1 - p_0) - \var(p_{t-1})}{2\var(p_t) - \var(p_{t-1})}
\end{align}
